A Fast and Tight Heuristic for A* in Road Networks

### 2021-09-30 paper/ch_potentials.tex
add bidir tables and scripting around them

% \usepackage{amssymb}
% \usepackage{amsmath}
% checkmarks
\usepackage{pifont} % TODO
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

@@

\subparagraph{Inputs and Methodology}
Our main benchmark instance is a graph of the road network of Germany obtained from Open Street Map\footnote{\url{https://download.geofabrik.de/europe/germany-200101.osm.pbf}}.
To obtain the routing graph, we use the import from RoutingKit\footnote{\url{https://github.com/RoutingKit/RoutingKit}}.
The graph has 16M nodes and 35M edges.
For this instance, we have proprietary traffic data provided by Mapbox\footnote{\url{https://mapbox.com}}.
The data includes a live traffic snapshot from Friday 2019/08/02 afternoon and comes in the form of 320K OSM node pairs and live speeds for the edge between the nodes.
It also includes traffic predictions for 38\% of the edges as predicted speeds for all five minute periods over the course of a week.
We exclude speed values which are faster than the freeflow speed computed by RoutingKit.
Additionally, we have two graphs with proprietary traffic predictions provided by PTV\footnote{\url{https://ptvgroup.com}}.
The PTV instances are not OSM-based.
One is an old instance of Germany with traffic predictions from 2006 for 7\% of the edges and the other one a newer instance of Europe with predictions for 27\% of the edges.
Table~\ref{tab:graphs} contains an overview over our instances.
In this table, we further include the sequential running time necessary to construct the CH.
We report preprocessing running times as averages over 10 runs.
For queries, we perform 10\,000 point-to-point queries where both source and target are nodes drawn uniformly at random and report average results.

\subparagraph{Experiments}

@@

\begin{table}
\centering
\caption{
TODO
}\label{tab:bidir_pruning}
\input{table/bidir_pruning.tex}
\end{table}

>>>>

% \usepackage{amssymb}
% \usepackage{amsmath}
\newcommand{\cmark}{$\bullet$}
\newcommand{\xmark}{$\circ$}

@@

\paragraph{Inputs and Methodology}
Our main benchmark instance is a graph of the road network of Germany obtained from Open Street Map\footnote{\url{https://download.geofabrik.de/europe/germany-200101.osm.pbf}}.
To obtain the routing graph, we use the import from RoutingKit\footnote{\url{https://github.com/RoutingKit/RoutingKit}}.
The graph has 16M nodes and 35M edges.
For this instance, we have proprietary traffic data provided by Mapbox\footnote{\url{https://mapbox.com}}.
The data includes a live traffic snapshot from Friday 2019/08/02 afternoon and comes in the form of 320K OSM node pairs and live speeds for the edge between the nodes.
It also includes traffic predictions for 38\% of the edges as predicted speeds for all five minute periods over the course of a week.
We exclude speed values which are faster than the freeflow speed computed by RoutingKit.
Additionally, we have two graphs with proprietary traffic predictions provided by PTV\footnote{\url{https://ptvgroup.com}}.
The PTV instances are not OSM-based.
One is an old instance of Germany with traffic predictions from 2006 for 7\% of the edges and the other one a newer instance of Europe with predictions for 27\% of the edges.
Table~\ref{tab:graphs} contains an overview over our instances.
In this table, we further include the sequential running time necessary to construct the CH.
We report preprocessing running times as averages over 10 runs.
For queries, we perform 10\,000 point-to-point queries where both source and target are nodes drawn uniformly at random and report average results.

\paragraph{Experiments}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_many_to_one.pdf}
\caption{
Many-to-One CH
}\label{fig:many_to_one}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_cch_many_to_one.pdf}
\caption{
Many-to-One CCH
}\label{fig:many_to_one_cch}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/lazy_rphast_many_to_many.pdf}
\caption{
Many-to-Many
}\label{fig:many_to_many}
\end{figure}

@@

\begin{table}
\centering
\caption{
TODO
OSM Ger, Weight Scaled uniformly by 1.05, alternating dirs
}\label{tab:bidir_pruning}
\input{table/bidir_pruning.tex}
\end{table}

\begin{table}
\centering
\caption{
TODO
OSM Ger, Weight Scaled 1.5, sym with improved pruning, avg without, with topo opt
}\label{tab:bidir_switching}
\input{table/bidir_switching.tex}
\end{table}

\begin{table}
\centering
\caption{
TODO
OSM Ger
}\label{tab:bidir}
\input{table/bidir.tex}
\end{table}
